---
title: "R markdown examples & templates"
author: "jgp"
date: "13 May 2020"
output:
  html_document:
  #ioslides_presentation:       # creates html slideshow
    toc: TRUE                   # add TOC; toc_float moves TOC to sidebar and makes look cooler
    toc_float:
      collpased: FALSE
      smooth_scroll: FALSE
    df_print: paged             # automatic way to format data tables
    theme: united               # adds theme to doc # https://www.datadreaming.org/post/r-markdown-theme-gallery/
    #tufte::tufte_html:default  # adds theme from tufte package, not currently working
    #rmdformats::material:      # adds theme from rmdformats package, nor currently owrking
    code_folding: show          # allows for optional hiding of code, shows be default
    #code_folding: hide         # allows for optional hiding of code, hides by default
---

# read in libraries

## no options
```{r}
library(dplyr)
```

## hide messages
```{r, message = FALSE}
library(dplyr)
```

## hide code
```{r, echo = FALSE}
library(tufte) # used to bring in additional rmd themes
library(prettydoc) # used to bring in additional rmd themes
library(rmdformats) # used to bring in additional rmd themes
```
#### <doesn't look like anything to me>

# read in data 

## from csv
```{r}
pop_by_zip <- read.csv("../01_data/pop-by-zip-code.csv") %>%
  rename(
    zip = "ï..zip"
  ) %>%
  mutate(
    zip = sprintf("%05g", zip)
  )

pop_by_zip
```
#### the formatting and display of the above code chunk is substantially improved by the knitr options <df_print: paged>

## read in dat from package
```{r}
library(zipcode)
data(zipcode)
dim_zip <- zipcode
rm(zipcode)
dim_zip
```

# do some maths

## manipulate 
```{r}
pop_by_state <- pop_by_zip %>%
  left_join(
    dim_zip
    ,by = "zip"
  ) %>%
  group_by(state) %>%
  summarize(pop = sum(y_2016, na.rm=T))
            
pop_by_state
  
```

# use inline r code

## these variables are dynamically from in memory data frame

#### the zip code `r pop_by_zip$zip[1]` has the population `r pop_by_zip$y_2016[1]`

# common options

eval TRUE         Whether to evaluate the code and include its results  
echo TRUE         Whether to display code along with its results  
warning TRUE      Whether to display warnings  
error FALSE       Whether to display errors  
message TRUE      Whether to display messages  
tidy FALSE        Whether to reformat code in a tidy way when displaying it  
results "markup"  "markup", "asis", "hold", or "hide"  
cache FALSE       Whether to cache results for future renders  
comment "##"      Comment character to preface results with  
fig.width 7       Width in inches for plots created in chunk  
fig.height 7      Height in inches for plots created in chunk  

## results
### default
```{r}
pop_by_state <- pop_by_zip %>%
  left_join(
    dim_zip
    ,by = "zip"
  ) %>%
  group_by(state) %>%
  summarize(pop = sum(y_2016, na.rm=T))
            
pop_by_state
```

### markup
```{r, results = 'markup'}
pop_by_state <- pop_by_zip %>%
  left_join(
    dim_zip
    ,by = "zip"
  ) %>%
  group_by(state) %>%
  summarize(pop = sum(y_2016, na.rm=T))
            
pop_by_state
```

### asis
```{r, results = 'asis'}
pop_by_state <- pop_by_zip %>%
  left_join(
    dim_zip
    ,by = "zip"
  ) %>%
  group_by(state) %>%
  summarize(pop = sum(y_2016, na.rm=T))
            
pop_by_state
```

### hold
```{r, results = 'hold'}
pop_by_state <- pop_by_zip %>%
  left_join(
    dim_zip
    ,by = "zip"
  ) %>%
  group_by(state) %>%
  summarize(pop = sum(y_2016, na.rm=T))
            
pop_by_state
  
```

### hide
```{r, results = 'hide'}
pop_by_state <- pop_by_zip %>%
  left_join(
    dim_zip
    ,by = "zip"
  ) %>%
  group_by(state) %>%
  summarize(pop = sum(y_2016, na.rm=T))
            
pop_by_state
  
```
